---
title: "R Notebook"
output: html_notebook
---

############################################################################
# TASK 1: DECATHLON DATA
############################################################################


# We load the necessary packages for the analysis
```{r}
library(readr)
library(here)
library(tidyverse)
library(janitor)
library(stringr)
```


# Storage the decathlon.rds file into an object, called "decathlon_data"
```{r}
decathlon_data <- read_csv("clean_data/decathlon_tidy_data.csv")
```




------------------------------------------------------------------------------
#                   Analysis questions
------------------------------------------------------------------------------

# Question 1. Who had the longest long jump seen in the data?
```{r}
decathlon_data_Q1 <- decathlon_data %>% 
  select(name, sports, scores) %>% 
  filter(sports == "long_jump") 

# we use the 'which.max' function who is applied to the column "scores". 
decathlon_data_Q1[which.max(decathlon_data_Q1$scores),]

```

# Question 2. What was the average 100m time in each competition?
```{r}
decathlon_data_Q2 <- decathlon_data %>% 
  select(competition, sports, scores) %>% 
  filter(sports == "100m") %>% 
  group_by(competition) %>% 
  summarise(mean(scores))

```


# Question 3. Who had the highest total points across both competitions?
```{r}
decathlon_data_Q3 <- decathlon_data %>% 
  group_by(name) %>% 
  summarise("total_points" = sum(points)) 

decathlon_data_Q3[which.max(decathlon_data_Q3$total_points),]

```





#Question 4.What was the shot-put scores for the top three competitors in each competition?
```{r}
decathlon_data_Q4 <- decathlon_data %>% 
    filter(sports == "shot_put") %>% 
    arrange(rank) 

# We get the first 6 observations (associated to the top three comptetitros)
decathlon_data_Q4 <- decathlon_data_Q4[c(1:6),]
           
```


# Question 5. What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?

```{r}
decathlon_data_Q5 <- decathlon_data %>% 
    filter(sports == "400m")

index1 <- which(decathlon_data_Q5$scores > 50)
index2 <- which(decathlon_data_Q5$scores < 50)


mean(decathlon_data_Q5$points[index1])
mean(decathlon_data_Q5$points[index2])


```      


