---
title: "R Notebook"
output: html_notebook
---

#############################################################################
#                           Data Cleaning Scripts
#############################################################################

# We load the necessary packages for the analysis
```{r}
library(readr)
library(here)
library(tidyverse)
library(janitor)
library(stringr)
```


# Storage the 'cake_ingredient_code.csv' file into an object, called "cake_ingredients_data"
```{r}
cake_ingredients_data <- read_csv("raw_data/cake-ingredients-1961.csv")
cake_ingredients_data
```


# Storage the 'cake_ingredient_code.csv' file into an object, called "cake_ingredients_data_code"
```{r}
cake_ingredients_code <- read_csv("raw_data/cake_ingredient_code.csv")
cake_ingredients_code
```


# We usew the 'pivot_longer' function to tidy up the given data. The new data is stored in an object called, "cake_ingredients_tidy_data".

# We also remove all the NAs from the new table
```{r}
cake_ingredients_tidy_data <- cake_ingredients_data %>% 
  pivot_longer(cols = c("AE":"ZH"), 
             names_to = "code", 
             values_to = "weight")

cake_ingredients_tidy_data<- cake_ingredients_tidy_data %>% 
  drop_na()
```


# We join the two tables together 
```{r}
# joining the two tables together, so the information is all in the same place. 
cake_ingredients_tidy_data <- left_join(cake_ingredients_tidy_data, 
                                     cake_ingredients_code, by = "code") 
```

# We remove the "code" column from the data
```{r}
cake_ingredients_tidy_data <- cake_ingredients_tidy_data %>% 
                           select(-code)
```


# We rename the "Cake" column to "cake" column
```{r}
names(cake_ingredients_tidy_data) <- c("cake", "weight", "ingredient","measure") 
names(cake_ingredients_tidy_data)
```

# We set strings to lowcasecase across the column "ingredient"
# We keep the cake names as it is because the names look consistent 
```{r}
cake_ingredients_tidy_data <- cake_ingredients_tidy_data %>% 
  mutate(ingredient = str_to_lower(ingredient))
```


# We now write the clean file and save it in the folder "clean_data" 
```{r}
write_csv(cake_ingredients_tidy_data, "clean_data/cake_ingredients_tidy_data.csv")
```




