---
title: "R Notebook"
output: html_notebook
---

### Probability Quiz

Load the required packages for this homework:
```{r}
library(prob)
library(gtools)
library(tidyverse)
```

*Question 1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?*
```{r}
# sample spaxce when you roll a dice once
sample_space_dice_once <- rolldie(1)

# number of possible outcomes if you want a number less than 5  
dice_less_than_five <- sample_space_dice_once %>% 
  filter(X1 < 5)

# probability of the outcome
nrow(dice_less_than_five) / nrow(sample_space_dice_once)
```

The probability of getting a number less than 5 when a dice is rolled once is 2/3 = 0.666.

*Question 2. How many outcomes are there in the sample space of an experiment in which we toss three dice?*
```{r}
# sample spaxce when you roll a dice three times
sample_space_dice_three <- rolldie(3)

sample_space_dice_three %>% 
  summarise(sample_spice = n())
```

There are 216 possible outcomes if a dice is rolled three times.

*Question 3. In an experiment where we roll four dice:*
1. how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)?
```{r}
# sample space when you roll a dice four times
sample_space_dice_four <- rolldie(4)

total_equals_5_6_7 <- sample_space_dice_four%>% 
mutate(colums_sum = X1 + X2 + X3 + X4) %>% 
filter(colums_sum == 5 | colums_sum == 6 | colums_sum == 7)

nrow(total_equals_5_6_7)
```

There are 34 outcomes where the summation of four dices will give either 5, 6 or 7.

2. what is the probability of this event?
```{r}
nrow(total_equals_5_6_7) /nrow(sample_space_dice_four)
```

The probability where the summation of four dices will give either 5, 6 or 7 is 0.03 (3 d.p.)

3. what assumptions do we apply in answering part iii?
In *Question 3*, it was assumed that a different event is occured when a dice is rolled,  e.g. the same number is apperead when a single dice is rolled.

*Question 4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?:*

```{r}
# create vector of choices contains five peple, n = 10. 
five_people <- c("Extreme Tall", "Very Tall", "Tall", "Medium Height", "Short")

# Choose a combination of 5, r = 5
possible_seats  <- as_tibble(permutations(n = 5, 
                                  r = 5, 
                                  v = five_people, repeats.allowed = FALSE))

# probability that the 5 people sit in order of decreasing height (only possible once):
1/nrow(possible_seats)
```

The probability that the five people sit in order of decreasing height is 0.008 (3 d.p).

*Question 5. I roll six dice:*
1. what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
```{r}
# sample space when you roll a dice six times
sample_space_dice_six <- rolldie(6)
nrow(sample_space_dice_six)

1/nrow(sample_space_dice_six)
```
2. what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?


*Question 6.If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?*
```{r}
cards_all <- cards()  
nrow(cards_all)


cards_spade <- cards_all %>% 
  filter(suit == "Spade")
probaA = nrow(cards_spade)/nrow(cards_all) # spade cards out of 52 

probaB = 1/2 # black cards out of 52

cards_black_spade <- probaA/ probaB 
cards_black_spade
```

The probability that the card is spade, from a black pack, is 0.5 

*Question 7.Eight patients: Alice, Bob, Carmen, Dinesh, Ella, Fergus, Gianna and Henry are waiting to see a doctor, but only five appointment slots are left today*
1. In how many different orders can the doctor see patients today?
```{r}
# create vector of eight patients five peple, n = 8
patients <- c("Alice", "Bob", "Carmen", "Dinesh", "Ella", "Fergus", "Gianna", "Henry")

# Choose a combination of 5, r = 5
possible_appointment  <- as_tibble(permutations(n = 8, 
                                  r = 5, 
                                  v = patients, repeats.allowed = FALSE))

# rename the variables in the 'possible_appointment' tible (not necessary for the study)
possible_appointment <- possible_appointment %>%
  rename(
    Slot_1 = V1,
    Slot_2 = V2,
    Slot_3 = V3,
    Slot_4 =V4,
    Slot_5 = V5
  )

nrow(possible_appointment)

```

There are 6720 different slots that the 8 patients can fill the 8 slots. 


2. What is the probability of Gianna and Danesh both being seen today?
```{r}
Gianna_and_Dinesh <- possible_appointment %>% 
  isin(c("Gianna","Dinesh"))

sum(Gianna_and_Dinesh)/nrow(possible_appointment)
```

There is a probability of 0.36 (2 d.p) that Gianna and Danesh will be seen today.

3. What is the probability of Gianna being seen before Dinesh today?
```{r}
Gianna_and_Dinesh_2 <- possible_appointment %>% 
  isin(c("Gianna","Dinesh"), ordered = TRUE)

ans1 <- sum(Gianna_and_Dinesh_2)/sum(Gianna_and_Dinesh) # provided they will both seen by the doctor
ans2 <- sum(Gianna_and_Dinesh_2)/nrow(possible_appointment) # provided they will not seen by the doctor
```

The probability of Giana being seen before Dinesh is 0.5, provided that they will both seen by the doctor. Alternative, Gianna has a probability of 0.18 seen by the doctor before Dinesh in case all 8 patients are in the waiting list. 


```{r}
# this should be half the probability of question ii, because, in filtered outcomes for 
# question ii., Gianna would be before Dinesh half the time.

# iv.
# first step is a 2P2 problem: permute 2 patients from 2.
high_priority_patients <- c("Carmen", "Henry")
S_high_priority <- as_tibble(permutations(n = 2, r = 2, v = high_priority_patients, repeats.allowed = FALSE))
names(S_high_priority) <- c("appt1", "appt2")

# second step is a 6P3 problem: permute 3 patients from 6.
normal_priority_patients <- c("Alice", "Bob", "Dinesh", "Ella", "Fergus", "Gianna")
S_normal_priority <- as_tibble(permutations(n = 6, r = 3, v = normal_priority_patients, repeats.allowed = FALSE))
names(S_normal_priority) <-c("appt3", "appt4", "appt5")

# merge these dataframes
S <- merge(S_high_priority, S_normal_priority)
# final answer
nrow(S)
```


*Question 8.If order is not significant, how many ways are there to select a 5 student quiz team from a group of 8 students?*
```{r}
# use the combination function, where we have 8 students and we need a combination of 5 students. 

# number of total students (assign by a number)
number_of_students <- 1:8

# use the combinations function
five_students_combi <- combinations(n = 8, r = 5, v = number_of_students)

# number of combinations
nrow(five_students_combi)
```

```{r}
# question 8 (alternative way) 
five_students_combi_2 <- choose(8, 5)
five_students_combi_2
```

*Question 9.How would your answer for question 8 change if a team captain had to be selected for each team?*
```{r}
# use the combination function, where we have 7 (out of 8) students and we need a combination of another 4 students to fill a team of 5. 

# number of total students (assign by a number)
number_of_students_2 <- 1:7

# use the combinations function
four_students_combi <- combinations(n = 7, r = 4, v = number_of_students)

nrow(four_students_combi)

# number of combinations
#nrow(five_students_combi)
```

This time, there are 35 combinations that can form a team of 5 out of 8 peple, provided one of those 8 students is always in the team.
