---
title: "R Notebook"
output: html_notebook
---

# Simple linear regression homework

```{r}
library(tidyverse)
library(janitor)
library(dplyr)
```



### Section 1: Residuals vs. leverage
Read this material on the leverage of points in regression, and how to interpret the Residuals vs Leverage diagnostic plot produced by plotting the lm() model object.


### Section 2: project_management analysis
The file project_management.csv contains data sampled from the recent work schedule of a small construction company. Column estimated_length contains the estimated length of a building job in days, while column actual_length contains the actual recorded length of the job in days.

**Load the data into a dataframe project**
```{r}
project <-read_csv("project_management.csv")
```

```{r}
project %>% 
glimpse()
```

```{r}
class(project)
```

```{r}
project <- as_data_frame(project)
class(project)
```


**Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.**
```{r}
project %>%
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point()
```


**Label the data points with their row number in the data frame using the command**
```{r}
text(project$estimated_length, project$actual_length, labels = seq(nrows(project)), cex = 0.7, pos = 2)
```




