#########################################################################################

##                                  PSQL LAB (Week2)

#########################################################################################

## Load the necessary libraries
```{r}
library(keyring)
library(RPostgreSQL)
```


## Connecting R to local database
```{r}
keyring_unlock("local")
username <- key_get("postgresql_username", keyring = "local") 
password <- key_get("postgresql_password", keyring = "local")
keyring_lock("local")
db_connect <- dbConnect(drv = PostgreSQL(), user = username, password = password, dbname = "omni_employees", host = "localhost")
rm(username, password)
```

---------------------------------------------------------------------------------------------
##                         PART 0: Read all the data
---------------------------------------------------------------------------------------------

We check which tables are included in the database. The dbListTables command help us to do so. We can use two different commands:
## Approach 1
```{r}
dbListTables(conn = db_connect)
```

Get all the data from omni_employees and storaged them in objects(vectors).
```{r}
employees_vect <- dbGetQuery(db_connect, 
           "SELECT *
           FROM employees ") 
pay_details_vect <- dbGetQuery(db_connect, 
           "SELECT *
           FROM pay_details ") 
teams_vect <- dbGetQuery(db_connect, 
           "SELECT *
           FROM teams ") 
committees_vect <- dbGetQuery(db_connect, 
           "SELECT *
           FROM committees ") 
employees_committees_vect <- dbGetQuery(db_connect, 
           "SELECT *
           FROM employees_committees ") 
```

We check which variables are included in table, 'employees'. The dbListFields command help us to do so. We can use two different commands:
## Approach
```{r}
dbListFields(conn = db_connect, name = "employees")
```

We can repeat it for the other data tables:
## Approach
```{r}
dbListFields(conn = db_connect, name = "employees_committees")
```

---------------------------------------------------------------------------------------------
##                         PART 1: MVP
---------------------------------------------------------------------------------------------




Question 1_1: Find all the employees who work in the ‘Human Resources’ department.

```{r}
dbGetQuery(db_connect, 
           "SELECT *
           FROM employees 
           WHERE department = 'Human Resources'") 
```

Question 1_2: Get the first name, last name, and country of the employees who work in the ‘Legal’ department
# Approach 1
```{r}
dbGetQuery(db_connect, 
           "SELECT first_name, last_name
           FROM employees 
           WHERE department = 'Legal'") 
```

# Approach 2
```{r}
dbGetQuery(db_connect, 
           "SELECT CONCAT(first_name, ' ',last_name) AS full_name_Legal_department
           FROM employees 
           WHERE department = 'Legal'") 
```

Question 1_3: Count the number of employees based in Portugal.
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT COUNT(*) AS employees_portugal
           FROM employees 
           WHERE country = 'Portugal'") 
```

Question 1_4:Count the number of employees based in either Portugal or Spain.
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT COUNT(*) AS employees_portugal_and_Spain
           FROM employees 
           WHERE country = 'Portugal' OR country = 'Spain'  ") 
```


Question 1_5: Count the number of pay_details records lacking a local_account_no.
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT COUNT(*) AS lacking_account_no
           FROM pay_details
           WHERE local_account_no IS NULL  ") 
```

The querry below is not needed but we double check to see how many iban numbers are missing from the data.
```{r}
dbGetQuery(db_connect, 
           "SELECT COUNT(*) AS lacking_iban
           FROM pay_details
           WHERE iban IS NULL  ") 
```

Question 1_6: Are there any pay_details record lacking both a local_account_no and iban number?
```{r}
dbGetQuery(db_connect, 
           "SELECT *
           FROM pay_details
           WHERE local_account_no IS NULL AND iban IS NULL ") 
```

Question 1_7: Get a list of employees first names and last names ordered alphabetically by their last name (put any nulls last).
# Approach 1
```{r}
dbGetQuery(db_connect, 
           "SELECT first_name, last_name
           FROM employees
           ORDER BY last_name NULLS LAST ") 
```
# Approach 2
```{r}
dbGetQuery(db_connect, 
           "SELECT CONCAT(first_name,' ', last_name) AS full_name
           FROM employees
           ORDER BY last_name NULLS LAST ") 
```

Question 1_8: Get a list of employees first names, last names and countries, ordered alphabetically first by their country and second by their last name (put any nulls last).
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT first_name, last_name, country
           FROM employees
           ORDER BY country NULLS LAST") 
```

Question 1_9: Find the top ten highest paid employees in the corporation..
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT *
           FROM employees
           ORDER BY salary DESC NULLS LAST LIMIT 10") 
```

Question 1_10: Find the first name, last name and salary of the lowest paid of the employees in Hungary.
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT first_name, last_name, salary, country
           FROM employees
           WHERE country = 'Hungary'
           ORDER BY salary ASC NULLS LAST LIMIT 1") 
```

Question 1_11: How many employees have a first name beginning with ‘F’?
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT *
           FROM employees
           WHERE first_name LIKE 'F%'") 
```

Question 1_12: Find all the details of any employees with a ‘yahoo’ e-mail address.
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT *
           FROM employees
           WHERE email LIKE '%yahoo%'") 
```

Question 1_13: Count the number of pension enrolled employees not based in either France or Germany.
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT COUNT(*) AS pension_enrol
           FROM employees
           WHERE pension_enrol = TRUE 
           AND (country != 'France' OR country != 'Germany')") 
```

```{r}
dbGetQuery(db_connect, 
           "SELECT COUNT(*) AS pension_enrol
           FROM employees
           WHERE country != 'France' AND country != 'Germany'") 
```

There are 488 peple enrol for the pension scheme.
```{r}
dbGetQuery(db_connect, 
           "SELECT *
           FROM employees
           WHERE pension_enrol = TRUE ") 
```

There are 29 peple coming from France.
```{r}
dbGetQuery(db_connect, 
           "SELECT *
           FROM employees
           WHERE country = 'France' ") 
```

There are 2 peple coming from Germany.
```{r}
dbGetQuery(db_connect, 
           "SELECT *
           FROM employees
           WHERE country = 'Germany' ") 
```


Question 1_15: What is the maximum salary among employees in the Engineering department who work 1.0 full-time equivalent hours?
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT MAX(salary)
           FROM employees
           WHERE department = 'Engineering' AND fte_hours = 1.00") 
```

Question 1_16: Obtain a count by department of the employees who started work with the corporation in 2003.
# Approach
```{r}
dbGetQuery(db_connect, 
           "SELECT department, COUNT(department) AS employees_department
           FROM employees
           WHERE start_date BETWEEN '2003-01-01' AND '2003-12-31'
           GROUP BY department") 
```