---
title: "R Notebook"
output: html_notebook
---

```{r}
library(CodeClanData)
library(tidyverse)
```

### Save the datadest into an objct
```{r}
game_sales <- game_sales
#view(game_sales)
```

### Dimension of the dataset
```{r}
dim(game_sales)
```

### Variables (columns) of the dataset
```{r}
names(game_sales)
```

```{r}
unique(game_sales$genre)
```


```{r}
unique(game_sales$publisher)
```

```{r}
unique(game_sales$developer)
```



```{r}
unique(game_sales$platform)
```


```{r}
game_sales %>% 
  select(name,publisher, developer, platform, sales) %>% 
  filter(publisher == "Nintendo") 
```


## Investigate the developers for Nintendo

### Find in percentage, which other companies develop games for Nintendo 
```{r}
game_sales_Nintendo <- game_sales %>% 
  select(name,publisher, developer, platform) %>% 
  filter(publisher == "Nintendo") %>% 
  group_by(developer) %>% 
  summarise(count = n()) %>% 
  mutate(percentage = round((count*100)/sum(count), 2))
```

### Plot the developer comapanies that developed games for the Nintendo
```{r}
game_sales_Nintendo <-
mutate(game_sales_Nintendo, developer = fct_reorder(developer, percentage))

game_sales_Nintendo %>% 
  ggplot()+
  aes(x= developer, y = percentage, fill = developer) +
  geom_col()+
  coord_flip()+
  labs(title = "Developer companies that are used to make games for Nintendo")
```


## Investigate the sales for Nintendo with respect to their developers
```{r}
game_sales_copies <- game_sales %>% 
  select(publisher, developer, year_of_release, sales) %>% 
  filter(publisher == "Nintendo") %>%
  group_by(developer) %>% 
  summarise(copies_sales_in_millions= sum(sales)) %>% 
  mutate(percentage = round((copies_sales_in_millions*100)/sum(copies_sales_in_millions), 4))
```

### Plot the developer comapanies that developed games for the Nintendo
```{r}
game_sales_copies<-
mutate(game_sales_copies, developer = fct_reorder(developer, percentage))

game_sales_copies %>% 
  ggplot()+
  aes(x= developer, y = percentage, fill = developer) +
  geom_col()+
  coord_flip()+
  labs(title = "Number of copies sold in percentage")
```



## Investigate the sales for Nintendo with respect to their plattforfs

### First find the number of games per platform
```{r}
game_per_platforms <- game_sales %>% 
  select(publisher, developer, sales, platform) %>% 
  filter(publisher == "Nintendo") %>%
  group_by(platform) %>%
  summarise(games_per_platform = n()) 

game_per_platforms
```

### Then find the numeber of sales per platform
```{r}
game_sales_platforms <- game_sales %>% 
  select(publisher, developer, sales, platform) %>% 
  filter(publisher == "Nintendo") %>%
  group_by(platform) %>%
  summarise(sales = sum(sales)) 

game_sales_platforms
```

# We join the two table
```{r}
platform_copies_and_sales <-left_join(game_per_platforms, game_sales_platforms, "platform")
platform_copies_and_sales
```

### Number of copies sold by platform
```{r}
platform_copies_and_sales %>% 
  ggplot()+
  aes(x= platform, y = sales) +
  geom_col() +
  labs(title = "Number of copies")
```

```{r}
game_sales %>% 
  filter(publisher == "Nintendo") %>% 
  ggplot()+
  aes(x= platform, y = sales, fill = genre) +
  geom_col() +
  labs(title = "Number of copies")
```


```{r}
game_sales %>% 
  filter(publisher == "Nintendo") %>% 
  ggplot()+
  aes(x= genre, y = sales, fill = platform) +
  geom_col() +
  labs(title = "sales with respect to genre")
```


## Relation between sales and critics
```{r}
game_sales %>% 
  filter(publisher == "Nintendo") %>% 
  ggplot()+
  aes(x= sales, y = user_score, colour = genre) +
  geom_point() #+
  #labs(title = "Number of copies")
```


