---
title: "R Notebook"
output: html_notebook
---

```{r}
library(CodeClanData)
library(tidyverse)
```


*Question 1. Pre-analysis.*


```{r}
backpack
```

The dimension of the considered dataset is 100 (observations) x 9 (variables) and is found by using the command:
```{r}
  dim(backpack)
```


The **backpack** dataset includes the following variables (or columns):   
```{r}
names(backpack)
```
A bried description of each variable:
1.The *backpack_weight* variable varies from 2 to 35.
2.The *body_weight* variable varies from 105 to 270.
3.The  *back_problems* variable is consisted from 0 and 1 values (0 = no back problems/1 = back problems?)
4.The  *year* variable varies from 0 to 6.
5.We considers femake and make observations (in the *sex* variable).
6.The *status* is consisted by two different notations, U (5 observations) and G (995)
7.The *units* variable varies from 0 to 18.
8. The *ratio* is estimated using the ratio between *backpack_weight* and *body_weight*.



Finally, the variables (columns) from the **backpack** dataset and their classification are shown in the table below:

| Integer         | Double | Character |
|-----------------|--------|-----------|
| backpack_weight | ratio  | major     |
| body_weight     |        | sex       |
| back_problems   |        | status    |
| year            |        |           |
| units           |        |           |



*Question 2. What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.*


By using a bar-chart plot, a positive- skewed distribution is observed for the *backpack weights* variable.
```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight),col = "white", fill = "red")
```



*Question 3.Are there differences in backpack weight between sex?*
In this example, the *postion = "dodge"* command is used in order to distinguish if there are any differences between male and female students in *backpack_weights*. As shown below, both males and females carry almsot the same weight of backpacks.
```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight, fill = sex), col = "white", position = "dodge") + 
  scale_colour_brewer()
```

We also use the the *postion = "fill"* command to see the differnce between the two genders. Once more, the graph shows that both genders havve almost same weight of backpacks.
```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight, fill = sex), col = "white", position = "fill") + 
  scale_colour_brewer()
```


Finally, the command below is used to calculate the mean value of the backpack weight. 
```{r}
backpack %>% 
  select(backpack_weight, sex) %>% 
  group_by(sex) %>% 
  summarise(mean_backpack_weight= mean(backpack_weight))

```


*Question 4.What is the relationship between body weight and backpack weight?*

In this example, we use a scatter plot to check if there is any correlation between students body_weight and their backpack_weight. As shown from the plot, there is no obvious relationship between the two variables since all the points are scatterd together. 
```{r}
ggplot(backpack) +
  geom_point(aes(x = backpack_weight, y = body_weight), colour = "red") 
```

The command below also shows that the *backpack weight*i varies randomly by increasing the *body weight* and therefore we can conclude that both variables have not any relationship.
```{r}
backpack %>% 
  select(body_weight, backpack_weight, ratio, sex) %>% 
  arrange(body_weight)
```



*Question 5.Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.?*

The above plot is revisited but this time the data points are associated with the *sex* variable. It is now clear to see that males have higher *body weight* in comparison to females. However, there is still no any difference between the bothe gender in regards to the *backpack weight*.
```{r}
ggplot(backpack) +
  geom_point(
    aes(x = backpack_weight, y = body_weight, colour = sex))
```

*Question 6.What proportion of students report back pain?*

Student that report back pain are denoted by the value of 1 whereas students without pain have value 0. 
The bar plot below shows that around 32-33% of students reported a back pain. 
```{r}
ggplot(backpack) +
  geom_bar(aes(x = back_problems), colour = "red") + 
  scale_colour_brewer()
```

*Question 7.Is this proportion different between men and women?*

The 25% of those students who report a back pain are males whereas the other 75% with a back pain are females. The plot below satisfies the results.

```{r}
ggplot(backpack) +
  geom_bar(aes(x = back_problems, fill = sex), position = "fill") + 
  scale_colour_brewer()
```


*Question 8.2:Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.*

NA


