#########################################################################################

##                                  HOMEWORK (Week_02_day_5)

#########################################################################################

## Load the necessary libraries
```{r}
library(keyring)
library(RPostgreSQL)
```


## Connecting R to local database
```{r}
keyring_unlock("local")
username <- key_get("postgresql_username", keyring = "local") 
password <- key_get("postgresql_password", keyring = "local")
keyring_lock("local")
db_connect <- dbConnect(drv = PostgreSQL(), user = username, password = password, dbname = "acme_employees", host = "localhost")
rm(username, password)
```

We check which tables are included in the database. The dbListTables command help us to do so. We can use two different commands:
## Approach 1
```{r}
dbListTables(conn = db_connect)
```

```{r}
employees_vect <- dbGetQuery(db_connect, 
           "SELECT *
           FROM employees") 
teams_vect <- dbGetQuery(db_connect, 
           "SELECT *
           FROM teams") 
feedbacks_vect <- dbGetQuery(db_connect, 
           "SELECT *
           FROM feedbacks") 
```

Question 1_1:Create a new data.frame containing the details of all employees held in the database
```{r}
employees_vect <- dbGetQuery(db_connect, 
           "SELECT * 
           FROM employees 
           ") 
```


Question 1_2:Retrieve the records for all employees again, but this time add a field full_name containing the first_name and last_name of each employee separated by a space.
# Approach 1
```{r}
employees_vect <- dbGetQuery(db_connect, 
           "SELECT *, CONCAT(first_name, ' ',last_name) AS full_name 
           FROM employees 
           ") 
```

Question 1_3: Retrieve the details of all employees again, but this time listing their team name (as team_name), rather than their team_id.
# Approach 1
```{r}
dbGetQuery(db_connect,
           "SELECT e.first_name, e.last_name, e.email, t.name AS team_name
           FROM employees AS e LEFT JOIN teams AS t
           ON e.team_id = t.id")
```

# Approach 1
```{r}
dbGetQuery(db_connect,
           "SELECT employees.first_name, employees.last_name, employees.email, teams.name             AS team_name
           FROM employees AS e LEFT JOIN teams AS t
           ON employees.team_id = teams.id")
```






