Reading in data homework

-------------------------------------------------
Part 1: MVP
-------------------------------------------------

```{r}
library(readr)
```


Question 1_1:Read in the state_income_data.csv file using the appropriate function.

```{r}
state_income_data <- read_csv("data/state_income_data.csv")
state_income_data
```


Question 1_2: How do you specify your own column names when using read_csv()?

```{r}
# We re-create the "sate_income_data vector" but this time we re-name the colum names. We store the new data into a vector, called "sate_income_data vector2". We only rename 3 columns

state_income_data2 <- read_csv("data/state_income_data.csv", 
                               col_names = c("Col1",
                                             "Col2",
                                             "Col3")
                               )
state_income_data2
```


Question 1_3: Read in the cars.csv file and use the col_types() function to ensure you load in:
```{r}
cars <- read_csv("data/cars.csv")
cars

# We now want to classify the variable (column) "vs as logical. We storage the results into an object called cars2
cars2 <- read_csv("data/cars.csv", col_types = cols(vs = col_logical()))
cars2
```

Question 1_4: Read in the scotland.txt file using the appropriate function.

```{r}
# The data file separates each variable with semi-colons. Therefore, we use the "read_delim" functions. It doesn't look like it works
scotland <- read_delim("data/scotland.txt", delim = ";")
scotland

scotland2 <- read_table("data/scotland.txt")
scotland2

scotland3 <- read_tsv("data/scotland.txt")
scotland3
```

Question 1_5: How do you read text into a one element character vector?

```{r}
char_vector <- read_lines("data/")
```

Question 1_6: Read in the steam-200k-sample.csv file. Fix any problems you may encounter.

```{r}
steam_sample <- read_csv("data/steam-200k-sample.csv", skip = 5, 
                         col_names = c("customer_id",
                                       "game_name",
                                       "what",
                                       "value",
                                       "bought_online"), col_types = cols(bought_online = col_logical())
                         )
steam_sample
```

Question 1_7: Read in the historic_eu_payments.tsv file.

```{r}
historic_payments <- read_tsv("data/historic_eu_payments.tsv")
historic_payments

```

Question 1_8: How do you read lines of text into a multi-element text vector?
```{r}

```


Question 1_9:
```{r}

```

Question 1_10:
```{r}

```


-------------------------------------------------
Part 2: Extension work
-------------------------------------------------

```{r}
sp


```



