---
title: "R Notebook"
output: html_notebook
---

# Homework - CIs

### Section 1: MVP
Now we’ll go back to CI creation in the normal fashion. We’ll take the 'ames' data from the CIs lab earlier today and regard it now as a sample, we won’t be drawing any smaller samples from within it. This is the usual situation in an analysis: you use all the data available to you!

```{r}
library(tidyverse)
library(janitor)
library(infer)
library(e1071)
```


*Load the data again, clean_names(), and re-familiarise yourself with it*

Let's get the dataset.
```{r}
ames <- read_csv("data/ames.csv")
ames <- clean_names(ames)
```



*Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?*
```{r}
ames %>% 
  select(lot_area) %>% 
  ggplot() +
  aes(x = lot_area) +
  geom_histogram(col="white", bins=30)
```

```{r}
ames %>% 
  select(lot_area) %>% 
  summarise(skewness_dist = skewness(lot_area, type =1))
```

The distirbution is unimodal and highly left-skewed.

*Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.*
First, let's get a sample from our dataset. We get a sample of 300 observations. 
```{r}
single_sample_300 <- ames %>% 
  rep_sample_n(size = 300, reps = 1) %>% 
  ungroup() %>% 
  select(lot_area)
```

Now, we will apply bootsrapping the single sample.
```{r}
bootstrap_rep_sample_300 <- single_sample_300 %>% 
  specify(response = lot_area) %>% 
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

```{r}
bootstrap_rep_sample_300 %>% 
  ggplot()+
  aes(x = stat)+
  geom_histogram(col = "white")
```


*Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution*

```{r}
bootstrap_lot_area_ci <- bootstrap_rep_sample_300 %>% 
  get_confidence_interval(level = 0.95, type = "percentile")
bootstrap_lot_area_ci
```


```{r}
bootstrap_rep_sample_300 %>% 
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = bootstrap_lot_area_ci)
```


*You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?*

```{r}
bootstrap_lot_area_ci_99 <- bootstrap_rep_sample_300 %>% 
  get_confidence_interval(level = 0.99, type = "percentile")
bootstrap_lot_area_ci_99
```


```{r}
bootstrap_rep_sample_300 %>% 
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = bootstrap_lot_area_ci_99)
```

It can be seen now that the confidence interval is wider, therefore there is higher possibility that the mean from our sampling will be included in the interval.

*Calculate the point estimate of the mean(lot_area)*

We also calculate the mean from our bootstrap sampling distribution. 
```{r}
bootstrap_rep_sample_300 %>%
  summarise(mean(stat))
```

### Section 2: Extension (Still working on it)

Calculate a point estimate and 95% CI for the proportion of houses in the data built before 1920. Does the number of reps you use matter? [Investigate reps from 200 up to 50000, memory of your laptop permitting]. 

First, let's rewrite the colulmn year_built into "Yes" (if houses build before 1920) or "No" otherwise.
```{r}
ames_old_houses <- ames %>% 
  mutate(year_built_new = ifelse(year_built < 1920, "Yes", "No")) 
```

Now, let's get a sample from our new column, called *ames_old_houses*. We get a sample of 200 observations.column **year_built**. 
```{r}
single_sample_year_built <- ames_old_houses %>% 
  rep_sample_n(size = 200, reps = 1)  
```

We now use bootstrap.
```{r}
bootstrap_rep_year_built <- single_sample_year_built %>%
  specify(response = year_built_new, success = "Yes") %>%
  generate(reps = 200, type = "bootstrap") %>%
  calculate(stat = "prop")
```

```{r}
bootstrap_prop_ci <- bootstrap_rep_year_built %>% 
  get_confidence_interval(level = 0.95, type = "percentile")
bootstrap_prop_ci
```

```{r}
bootstrap_rep_year_built %>% 
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = bootstrap_prop_ci)
```


We also calculate the mean from our bootstrap sampling distribution. 
```{r}
bootstrap_rep_year_built %>%
  summarise(mean(stat))
```

** We now repeat the proces with more reps, for example 1000 times. Then with 2000, 3000 and so on, up t0 5000 times**